### 2016-07-01 lineups.Rnw
barchart uploaded

\hh{Can we derive measures from the model estimates or the visual representation (ie. the network structure) that help us determine which lineups are more difficult than others, i.e. based on these estimates, how relaibly can we predict which panel will be picked from a lineup? 
XXX For that, we could also calculate the number of JTTs in each network - use `jtt` for that.}

>>>>

\hh{Big goal: Can we derive measures from the model estimates or the visual representation (ie. the network structure) that help us determine which lineups are more difficult than others, i.e. based on these estimates, how relaibly can we predict which panel will be picked from a lineup? 
XXX For that, we could also calculate the number of JTTs in each network - use `jtt` for that.}

\hh{Littler goal: evaluate pilot study and see whether the results line up with the conjectures made in the previous section.}

\hh{The pilot study consisted of an evaluation of a set of 20 lineups by 11 volunteers. For each of the model situations ($M_1$ vs $M_2$, $M_2$ vs $M_1$, $M_1$ vs $M_3$ and $M_3$ vs $M_1$) on lineup of size $m = 3, 6, 9, 12$ was used.}
\paragraph{Suitability of $M_3$ in lineups:}
\begin{figure}
\centering
<<data-picks, echo=FALSE, fig.width=10, fig.height=5, out.width='0.85\\linewidth'>>=
pdffiles <- dir("GGExperimentApr28/", pattern="pdf")
pdffiles <- gsub(".pdf","",pdffiles)
#pdffiles <- gsub("-m","",pdffiles)
#pdffiles <- gsub("-rep","",pdffiles)

dframe <- strsplit(pdffiles, split=" ") %>% plyr::ldply(function(x) x)
names(dframe) <- c("stimulus", "lineupid")

results <- read.csv("GGExperimentApr28/responses_GGExpApr28.csv")
lus <- results %>% group_by(Lineup, ChosenLU) %>% summarize(
  tally = n(),
  data = Answer[1],
  reason = paste(Reasoning, collapse="|")
)
names(lus)[2] <- "panel"

dframe_res <- merge(dframe, lus, all=TRUE, by.x="stimulus", by.y="Lineup")
dframe_res$data_pick <- with(dframe_res, data==panel)
dframe_res$model <- factor(gsub("(.*)-m.*", "\\1", dframe_res$lineupid))
levels(dframe_res$model) <- c("M1 vs M2",  "M1 vs M3", "M3 vs M1", "M2 vs M1")
dframe_res$model <- factor(dframe_res$model, levels = c("M1 vs M2",  "M2 vs M1", "M1 vs M3", "M3 vs M1"))
dframe_res$label <- gsub(".*-(m.*)", "\\1", dframe_res$lineupid)

dframe_res$data_pick <- factor(dframe_res$data_pick, levels=c("TRUE", "FALSE"))
dframe_res$res <- factor(dframe_res$data_pick, levels=c("TRUE", "FALSE"))
qplot(label, weight=tally, fill=data_pick, data=dframe_res) +
  facet_grid(.~model, scales="free", space="free") + theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1)) + 
  scale_fill_brewer("Data panel chosen", palette="Set1", na.value="grey80") 
@
\caption{\label{fig:data-picks}Barchart summarizing the number of responses from the pilot study by model and lineup. Color shows the number of times the data panel was chosen from the lineup. Clearly, the first two sets of lineups ($M_1$ vs $M_2$ and $M_2$ vs $M_1$) have on average higher number of data identifications. }
\end{figure}

\hh{Figure~\ref{fig:data-picks} shows barcharts of responses from the pilot study distinguishing the}
\hh{It is more difficult to identify the data plot in lineups of graphs based on data from models $M_1$ and $M_3$ than  in lineups of graphs based on data from models $M_1$ and $M_2$.
}
